Kyoto VR MQP Paper First Draft

### 2019-09-22 paper.tex
added diagram

>>>>

\subsubsection{Unit Testing ARuko}
\label{sec:unitTestingARuko}

The UI and AR features of the app are very important to the user experience. At
the same time, ARuko is not as purely graphical as it may seem. There is a
significant amount of ``business logic'' that interprets the tour from the
Editour file. On top of this, the geometric checks to test whether the user is
inside a particular arbitrarily-defined geographic region are very important to
get right.  Using Unity's built-in NUnit unit-testing framework, we wrote tests
to verify whether the tour data was being parsed correctly, and whether the tour
would be run correctly.

As a reminder, regions that trigger audio can be a set of three or more points
that define a closed polygon. Using the user's GPS location, the app needs to
periodically run a check to see if the user is located within one of those
polygons, which can be either concave or convex.

One decent algorithm for accomplishing this is by drawing a ray from a given
point to infinity. Barring edge cases (which will be discussed shortly) the
point is inside the polygon if the ray passes through an even number of line
segments.  The point is outside of the polygon if the ray intersects an odd
number of times. Figure~\ref{fig:intersectionsDiagram} should make it clear why
this works. This algorithm runs in $O(n)$, where $n$ is the sum total of the
number of vertices of all of the polygons being tested
~\autocite{geeksforgeekspolygon}.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{intersections-diagram.png}
	\caption{A visualization of the algorithm}
	\label{fig:intersectionsDiagram}
\end{figure}

For this, we implemented a few mathematical functions for individual parts of
the algorithm, such as testing for intersection. We wrote unit-tests to test
each part of the algorithm, so we could be confident that the GPS component of
the app would correctly place users into the correct regions.

There is one edge case where this algorithm has difficulties. If the ray that
is drawn for testing intersections passes directly through a vertex, the
algorithm will count two intersections instead of just one. Even though this is
highly unlikely considering our use case, we decided that our algorithm should
be robust enough to handle this on a matter of principle. Unit-testing helped us
catch and deal with this edge case.
